Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)

### 2018-09-25 paper/paper.Rmd
added sentence
moving legend

hamby224_test_explain %>%
  filter(set == "1") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(midpoint = 0)

>>>>

hamby224_test_explain %>%
  filter(set == "1") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(feature ~ label, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "bottom") +
  ylab("Feature Sets")
